Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
more precise explanation.
adding references.

For this purpose,
we brought design methods from other programming language communities and
integrated them with a Haskell-original test method.
In particular, we introduced {\tt doctest} and
integrated with QuickCheck. 
We also implemented {\tt hspec} with QuickCheck enabled.

@@

@@

We insist that examples and properties, which are useful for users, should be
documented.
So, let us first observe Haddock (version 2.7.2 or earlier), the documentation system of Haskell. 
Haddock defines annotation syntax in Haskell's comment.

@@

To test properties, we also uses GHCi. 
The `quickCheck'' string is prepended to each property
and GHCi evaluates it.
Success or failures is decided according to result string from GHCi.

@@

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

>>>>

For this purpose,
we brought design methods from other programming language communities and
integrated them with a Haskell-original test method.
In particular, we introduced {\tt doctest}~\cite{doctest} and
integrated with QuickCheck~\cite{quickcheck}. 
We also implemented {\tt hspec} inspired by rspec~\cite{rspec} 
and integrated with QuickCheck.

@@

TBD: behavior would not be a proper word since Haskell's pure
functions are very static.

@@

We insist that examples and properties, which are useful for users, should be
documented.
So, let us first observe Haddock~\cite{haddock} (version 2.7.2 or earlier), the documentation system of Haskell. 
Haddock defines annotation syntax in Haskell's comment.

@@

To test properties, we also uses GHCi. 
Each property is enclosed with 
the ``\verb|quickCheck (|'' and ``\verb|)|'' string
and GHCi evaluates it.
Success or failures is decided according to result string from GHCi.

@@

\bibitem[Claessen et al. 2000]{quickcheck}
Claessen K. and Hughes J., 
``QuickCheck: a lightweight tool for random testing of Haskell programs'',
ICFP '00 Proceedings of the fifth ACM SIGPLAN international conference on Functional programming,
pp 268 -- 279,
2000

\bibitem[Marlow et al. 2010]{haddock}
Marlow S. and Waern D.,
``Haddock User Guide'',
URL http://www.haskell.org/haddock/doc/html/,
2010

\bibitem[Python 2012]{doctest}
Python Software Foundation, 
``Python documentation'', 
URL http://docs.python.org/library/doctest.html,
2012

\bibitem[Chelimsky et al. 2010]{rspec}
Chelimsky D.,
Astels D., Dennis Z., Hellesoy A., Helmkamp B., and North D.,
``The RSpec Book: Behaviour-Driven 
Development with RSpec, Cucumber, and Friends'',
2010
%% Hellesoy -- o/
